---
title: "DATS6101 Group Project: Airbnb in New York City 2019"
author: "CrystalMath: Gregg Berne Legarda, Moncrief Russell, Nguyen Curtis, Satetasakdasiri Sanhanat, Bin Xing"
date: "October 15, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
```

```{r basicfcn, include=F}
# Knit does not work with install.packages functions. Any install.packages statements in the RMD file needs to be commented out before knitting. 
# And if the RMD is sent to another person/computer that requires installing the package, the user can remove the commenting and install the package.
# Here, we use another option by introducting this convenient function, we named it loadPkg(), which uses install.packages() and require(). 
# The function require() is similar to library(), except it returns a TRUE/FALSE value.
# You can add quietly=T option to the require() function
loadPkg = function(x) { if (!require(x,character.only=T, quietly =T)) { install.packages(x,dep=T,repos="http://cran.us.r-project.org"); if(!require(x,character.only=T)) stop("Package not found") } }
```

## Chapter 1: Introduction

New York city Is one of the most famous cities in the United States as it is financial, cultural and entertainment centers of the world. Of course, all of these factors are an attraction for tourists around the world to travel to New York. According to Mastercard Global Destination Index report, New York City is one of the 10 Most Visited Cities in 2019. There were 13.6 million foreign tourists that traveled to New York last year. In addition, they visited New York on an average of approximately 8 nights and spent an average of 152 dollars per day.  

Airbnb is a way of international visitors to find accommodations for traveling abroad. In 2018, Airbnb has approximately 150 million guest users and 2.9 million hosts around the world, covering in over 191 countries. According to Wachsmuth et al. (2018), New York is the third-largest Airbnb market in the world, with more than 40,000 housing and apartment rental listings, covering in Manhattan, Bronx, Queens, Brooklyn, and Staten Island. Furthermore, they found that New York’s Airbnb revenue increased by 14 percent or jumped to $657 million between 2016 and 2017, in line with an increase of the number of Airbnb guests and New York’s visitors. Taking into an account of all factors, it is undeniable that Airbnb has become a way to find the accommodations in New York City for many tourists around the world. Thus, Airbnb hosts data becomes a hot topic to do the research.

This report, focuses on Airbnb hosts in New York City 2019, contains 6 chapters: chapter 2 includes source data and basic data visualization; chapter 3 give descriptive statistics with raw and cleaned data; chapter 4 do the Linear Regression to predict the price; chapter 5 summarizes the relationship between price with Neighborhood Groups and Room Types; chapter 6 summarizes the relationship between availabilty with Neighborhood Groups and Room Types; chapter 7 is the report conclusion.

## Chapter 2: Description of Data

### 2.1 Source Data

In this study, the CSV data file comes from Inside Airbnb (http://insideairbnb.com/get-the-data.html). This dataset contains 48,865 Airbnb rental providers information in New York City 2019 with 16 variables,including housing ID,  accommodation name, host names, host ID, neighborhood group, sub-neighborhoods, latitude, longitude, room type, price, minimum night for rent, the number of reviews, the date of last review, the frequency of reviews, calculated host listing counts, and the number of availabilities in one year. To review the data, str() function in R is used to view a quick snapshot of the data as follows: 

```{r source data, echo=F}
library(readr)
AB_NYC <- read.csv("AB_NYC_2019.csv")
str(AB_NYC)

```

### 2.2 Geographic Coverage of Data

To do a basic data visualization, latitude and longitude in the dataset are used to draw the map, which is plotted by leaflet library in R. 

```{r in, include=F}
library(leaflet)

AB1 <- subset(AB_NYC, price %in% 0:150)
AB2 <- subset(AB_NYC, price %in% 151:500)
AB3 <- subset(AB_NYC, price %in% 501:1000)
AB4 <- subset(AB_NYC, price >= 1001)

AB5 <- subset(AB_NYC, room_type == "Private room")
AB6 <- subset(AB_NYC, room_type == "Entire home/apt")
AB7 <- subset(AB_NYC, room_type == "Shared room")

```

##### (1) New York's Airbnb with four different price groups.

To begin with first data visualization reviews, Airbnb hosts are divided by four different price groups to plot the map. Focusing on the below map, the number of Airbnb hosts that are lower than $150 per night (yellow points) are 33,957, accounting for 69.4% of all Airbnb hosts in New York City. In addition, there are 13.894 hosts or 28.4% that are in $151-$500 per night groups (blue points). Furthermore, 805 and 239 hosts are in $501-$1,000 (green points) and higher $1,000 (red points) groups, respectively.          

```{r map1, echo=F}
m <- leaflet(AB_NYC) %>%
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
  setView(-73.930000, 40.73500, zoom = 10) %>% 
  addCircleMarkers(lng=AB1$longitude, lat=AB1$latitude, popup=AB1$name, weight = 3,radius=2, color= "#ffa500", stroke = F, fillOpacity = 0.5) %>%
  addCircleMarkers(lng=AB2$longitude, lat=AB2$latitude, popup=AB2$name, weight = 3,radius=2, color= "#1337ed", stroke = F, fillOpacity = 0.5) %>%
  addCircleMarkers(lng=AB3$longitude, lat=AB3$latitude, popup=AB3$name, weight = 3,radius=2, color= "#79de76", stroke = F, fillOpacity = 0.5) %>%
  addCircleMarkers(lng=AB4$longitude, lat=AB4$latitude, popup=AB4$name, weight = 3,radius=2, color= "#cf2323", stroke = F, fillOpacity = 0.5) %>%
  addLegend("bottomright", colors= c("#ffa500", "#1337ed","#79de76","#cf2323"), labels=c(" < $150", "$151-$500", "$501-$1,000","> $1,000"), title="Price (US dollar)") 

m


```

##### (2) New York's Airbnb with three different room types.

Airbnb hosts can list entire homes/apartments, private or shared rooms. According to the below map, there are 25,409 hosts for entire homes/apartments (blue points), accounting for approximately 51.9% of all Airbnb hosts in New York City. While, there are 22,326 private rooms (yellow points) and only 1,160 shared rooms (red points).  

```{r map2, echo=F}
m <- leaflet(AB_NYC) %>%
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
  setView(-73.930000, 40.73500, zoom = 10) %>% 
  addCircleMarkers(lng=AB5$longitude, lat=AB5$latitude, popup=AB5$name, weight = 3,radius=2, color= "#ffa500", stroke = F, fillOpacity = 0.5) %>%
  addCircleMarkers(lng=AB6$longitude, lat=AB6$latitude, popup=AB6$name, weight = 3,radius=2, color= "#1337ed", stroke = F, fillOpacity = 0.5) %>%
  addCircleMarkers(lng=AB7$longitude, lat=AB7$latitude, popup=AB7$name, weight = 3,radius=2, color= "#cf2323", stroke = F, fillOpacity = 0.5) %>%
   addLegend("bottomright", colors= c("#ffa500", "#1337ed","#cf2323"), labels=c("Private room", "Entire home & apartment", "Shared room"), title="Room type") 

m


```














## Chapter 3: Descriptive Statistics

``` {r ch3, include=FALSE}

library(dplyr)
library("corrplot")


```

``` {r , echo=FALSE}
df<-read.csv("AB_NYC_2019.csv", header=TRUE)
```

``` {r , echo=FALSE}
str(df)
names(df)
````

``` {r , echo=FALSE}
summary(df)

```




``` {r qqnorm, echo=FALSE}
qqnorm(df$price, main = "price Q-Q plot", ylab="price quantiles")
qqline(df$price)

qqnorm(df$number_of_reviews,main = "Number of reviews Q-Q plot", ylab="number of reviews quantiles")
qqline(df$number_of_reviews)

qqnorm(df$availability_365, main = "availability 365 Q-Q plot", ylab="availability 365 quantiles")
qqline(df$availability_365)
````

``` {r plots, echo=FALSE}
plot(df$price, df$availability_365, main="Price and avalability", ylab="price", xlab="avalability", col=c("#ff0000","#00ff00","#0000ff","#ffff00") )

plot(df$price, df$number_of_reviews, main="Price and number of reviews", ylab="price", xlab="number of reviews", col=c("#ff0000","#00ff00","#0000ff","#ffff00") )
````

```{r outlierKD_def, include=FALSE}
# modified to allow prompt-free run-through
outlierKD <- function(dt, var, rmv=NULL) { 
     var_name <- eval(substitute(var),eval(dt))
     na1 <- sum(is.na(var_name))
     m1 <- mean(var_name, na.rm = T)
     sd1 <- sd(var_name,na.rm = T)
     par(mfrow=c(2, 2), oma=c(0,0,3,0))
     boxplot(var_name, main="With outliers")
     hist(var_name, main="With outliers", xlab=NA, ylab=NA)
     outlier <- boxplot.stats(var_name)$out
     mo <- mean(outlier)
     var_name <- ifelse(var_name %in% outlier, NA, var_name)
     boxplot(var_name, main="Without outliers")
     hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
     title("Price", outer=TRUE)
     na2 <- sum(is.na(var_name))
     cat("Outliers identified:", na2 - na1, "n")
     cat("Propotion (%) of outliers:", round((na2 - na1) / sum(!is.na(var_name))*100, 1), "n")
     cat("Mean of the outliers:", round(mo, 2), "n")
     m2 <- mean(var_name, na.rm = T)
     cat("Mean without removing outliers:", round(m1, 2), "n")
     cat("Mean if we remove outliers:", round(m2, 2), "n")
     #
     if(is.null(rmv)) { 
       response <- readline(prompt="Do you want to remove outliers and to replace with NA? [yes/no]: ") 
     } else {
       if (rmv=='y'|rmv=='yes'|rmv=='Y'|rmv=='Yes'|rmv=='YES'|rmv==TRUE ) { response = 'y' } else { response = 'n' }
     }
     #
     if(response == "y" | response == "yes"){
          dt[as.character(substitute(var))] <- invisible(var_name)
          assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
          cat("Outliers successfully removed", "n")
          return(invisible(dt))
     } else{
          cat("Nothing changed", "n")
          return(invisible(var_name))
     }
}
```

``` {r outliers, echo=FALSE}
outlierKD(df, price, 'y')
summary(df$price)
```

```{r outlier_reviews, include=FALSE}
# modified to allow prompt-free run-through
outlier_reviews <- function(dt, var, rmv=NULL) { 
     var_name <- eval(substitute(var),eval(dt))
     na1 <- sum(is.na(var_name))
     m1 <- mean(var_name, na.rm = T)
     sd1 <- sd(var_name,na.rm = T)
     par(mfrow=c(2, 2), oma=c(0,0,3,0))
     boxplot(var_name, main="With outliers")
     hist(var_name, main="With outliers", xlab=NA, ylab=NA)
     outlier <- boxplot.stats(var_name)$out
     mo <- mean(outlier)
     var_name <- ifelse(var_name %in% outlier, NA, var_name)
     boxplot(var_name, main="Without outliers")
     hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
     title("number_of_reviews", outer=TRUE)
     na2 <- sum(is.na(var_name))
     cat("Outliers identified:", na2 - na1, "n")
     cat("Propotion (%) of outliers:", round((na2 - na1) / sum(!is.na(var_name))*100, 1), "n")
     cat("Mean of the outliers:", round(mo, 2), "n")
     m2 <- mean(var_name, na.rm = T)
     cat("Mean without removing outliers:", round(m1, 2), "n")
     cat("Mean if we remove outliers:", round(m2, 2), "n")
     #
     if(is.null(rmv)) { 
       response <- readline(prompt="Do you want to remove outliers and to replace with NA? [yes/no]: ") 
     } else {
       if (rmv=='y'|rmv=='yes'|rmv=='Y'|rmv=='Yes'|rmv=='YES'|rmv==TRUE ) { response = 'y' } else { response = 'n' }
     }
     #
     if(response == "y" | response == "yes"){
          dt[as.character(substitute(var))] <- invisible(var_name)
          assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
          cat("Outliers successfully removed", "n")
          return(invisible(dt))
     } else{
          cat("Nothing changed", "n")
          return(invisible(var_name))
     }
}
```

```{r outlierKD_reviews, echo=FALSE}
outlier_reviews(df, number_of_reviews, 'y')
summary(df$number_of_reviews)
```

```{r outlier_availability, include=FALSE}
# modified to allow prompt-free run-through
outlier_availability <- function(dt, var, rmv=NULL) { 
     var_name <- eval(substitute(var),eval(dt))
     na1 <- sum(is.na(var_name))
     m1 <- mean(var_name, na.rm = T)
     sd1 <- sd(var_name,na.rm = T)
     par(mfrow=c(2, 2), oma=c(0,0,3,0))
     boxplot(var_name, main="With outliers")
     hist(var_name, main="With outliers", xlab=NA, ylab=NA)
     outlier <- boxplot.stats(var_name)$out
     mo <- mean(outlier)
     var_name <- ifelse(var_name %in% outlier, NA, var_name)
     boxplot(var_name, main="Without outliers")
     hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
     title("availability_365", outer=TRUE)
     na2 <- sum(is.na(var_name))
     cat("Outliers identified:", na2 - na1, "n")
     cat("Propotion (%) of outliers:", round((na2 - na1) / sum(!is.na(var_name))*100, 1), "n")
     cat("Mean of the outliers:", round(mo, 2), "n")
     m2 <- mean(var_name, na.rm = T)
     cat("Mean without removing outliers:", round(m1, 2), "n")
     cat("Mean if we remove outliers:", round(m2, 2), "n")
     #
     if(is.null(rmv)) { 
       response <- readline(prompt="Do you want to remove outliers and to replace with NA? [yes/no]: ") 
     } else {
       if (rmv=='y'|rmv=='yes'|rmv=='Y'|rmv=='Yes'|rmv=='YES'|rmv==TRUE ) { response = 'y' } else { response = 'n' }
     }
     #
     if(response == "y" | response == "yes"){
          dt[as.character(substitute(var))] <- invisible(var_name)
          assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
          cat("Outliers successfully removed", "n")
          return(invisible(dt))
     } else{
          cat("Nothing changed", "n")
          return(invisible(var_name))
     }
}
```

```{r outlierKD_availability, echo=FALSE}
outlier_availability(df, availability_365, 'y')
summary(df$availability_365)
```



``` {r matrix, echo=FALSE}
df.omitted<-na.omit(df)

df_num <- select(df.omitted, price, minimum_nights, number_of_reviews, reviews_per_month, calculated_host_listings_count, availability_365)

dfcor = cor(df_num) # get the correlation matrix between all numerical variables.
dfcor

corrplot(dfcor, method = "number")


```






## Chapter 4: Linear Regression
```{r setup1, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
#setwd('/users/russell/desktop/economics/dats 6101/project1')
#getwd()
```

```{r data, include=F}
nyc <- read.csv("AB_NYC_2019.csv", header = TRUE) #load data
```


 
```{r outliet, include=F}

outlierKD(nyc, price,'y')
summary(nyc$price)

outlierKD(nyc, minimum_nights,'y')
summary(nyc$minimum_nights)

```

```{r na, echo=F}
nyc4 <- na.omit(nyc)
summary(nyc4)
```
### 4.1 Linear Regression
#### Smart Question: How do minimum night, number of reviews, reviews per month, calculated host listings count and availability predict price?
```{r regress, echo=F}
barcolors = c("green", "violet", "orange", "blue", "pink", "red", "yellow", "cyan")
loadPkg("car")
model.final <- lm(price~minimum_nights+number_of_reviews+reviews_per_month+calculated_host_listings_count+availability_365,data=nyc4)
summary(model.final)
vif(model.final)
model.res <- resid(model.final)
hist(model.res, main="Histogram of Residuals", xlab="Regression Residuals", ylab="Frequency", col=barcolors)

```

All variables except number_of_reviews are statistically significant at the one percent level. The intercept suggests that 107 dollars is the mean price of an Air B&B.  The coefficent on minimum_nights suggests that a one unit increase in the minimum number of nights increases the price by 3.58 dollars.  The coefficient on reviews_per_month suggests that a one unit increase in reviews per month decreases price by 1.09 dollars. The coefficient on calculated_host_listings_count suggests that a one unit increase in the count of calculated host listings increases price by .31 cents. The coefficient on availability_365 suggests that a one unit increase in availability throughout the year increases price by .01 cents. The VIF test suggests that multicollinearity is not a concern in this linear model.








## Chapter 5: Neighbourhood Groups, Room Types and Price
Airbnb is frequently depicted as a better option for travelers looking for lower-cost accommodations. However, as Airbnb provides only a peer-to-peer exchange platform and does not set the prices directly, the hosts make their own decisions on prices when renting out their homes. In this chapter, we look at the price differences of Airbnb homes in New York City across neighbourhood groups and room types. Prices are in dollars. 

### 5.1 SMART Question
####Are there differences in Airbnb home prices across New York city neighbourhood groups and room types? 

### 5.2 Is there a difference in mean Airbnb home price among NYC Neighbourhood Groups?
####H0: There is no difference in mean Airbnb home price among NYC Neighbourhood Groups.
####H1: There is a difference in mean Airbnb home price among NYC Neighbourhood Groups.
There are five neighbourhood groups (boroughs) in this dataset: 
(1) Manhattan: the smallest yet most densely populated borough. It is considered the economic hub of the United States and even of the world.
(2) Brooklyn: the most populous borough.
(3) Queens: the largest borough and also the second most populous.
(4) Bronx: much of the borough is open space.
(5) Staten Island: the least populated borough.
Because the economic condition, density of population, and usage of land (and many other factors) are different among the five neighbourhood groups, we expect to find significant differences in Airbnb home prices. We use ANOVA to test this hypothesis. Below are the summary of the results.

```{r, include=FALSE}
#Import the dataset. Subset "Price", "Neighbourhood Group", and "Room Type" from the dataset.
data <- read.csv("AB_NYC_2019.csv")
d <- data[c(5, 9, 10)]
summary(d)
```

```{r, include=FALSE}
#Create a function to eliminate outliners.
outlierKD <- function(dt, var, rmv=NULL) { 
     var_name <- eval(substitute(var),eval(dt))
     na1 <- sum(is.na(var_name))
     m1 <- mean(var_name, na.rm = T)
     sd1 <- sd(var_name,na.rm = T)
     par(mfrow=c(2, 2), oma=c(0,0,3,0))
     boxplot(var_name, main="With outliers")
     hist(var_name, main="With outliers", xlab=NA, ylab=NA)
     outlier <- boxplot.stats(var_name)$out
     mo <- mean(outlier)
     var_name <- ifelse(var_name %in% outlier, NA, var_name)
     boxplot(var_name, main="Without outliers")
     hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
     title("Outlier Check", outer=TRUE)
     na2 <- sum(is.na(var_name))
     cat("Outliers identified:", na2 - na1, "n")
     cat("Propotion (%) of outliers:", round((na2 - na1) / sum(!is.na(var_name))*100, 1), "n")
     cat("Mean of the outliers:", round(mo, 2), "n")
     m2 <- mean(var_name, na.rm = T)
     cat("Mean without removing outliers:", round(m1, 2), "n")
     cat("Mean if we remove outliers:", round(m2, 2), "n")
     #
     if(is.null(rmv)) { 
       response <- readline(prompt="Do you want to remove outliers and to replace with NA? [yes/no]: ") 
     } else {
       if (rmv=='y'|rmv=='yes'|rmv=='Y'|rmv=='Yes'|rmv=='YES'|rmv==TRUE ) { response = 'y' } else { response = 'n' }
     }
     #
     if(response == "y" | response == "yes"){
          dt[as.character(substitute(var))] <- invisible(var_name)
          assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
          cat("Outliers successfully removed", "n")
          return(invisible(dt))
     } else{
          cat("Nothing changed", "n")
          return(invisible(var_name))
     }
}
```

```{r, include=FALSE}
outlierKD(d, price,'y') #Eliminate outliers.
```

```{r, include=FALSE}
d1 <- na.omit(d) #Eliminate NAs
summary(d1) #Check the summary statistics of d1
```

```{r, echo=FALSE}
#Run ANOVA test
anovad1 <- aov(price ~ neighbourhood_group, data=d1)
summary(anovad1)
```
As we can see from the ANOVA table above, F(4, 44665) = 1427, p < .001. Since the p-value is much smaller than a significance level of 0.05, we reject the null hypothesis that there is no difference in the means of Airbnb home prices among NYC Neighbourhood Groups and conclude that there is a significant difference in  mean Airbnb home prices among NYC Neighbourhood Groups.

```{r, echo=FALSE}
#Box plot with multiple neighbourhood groups
#install.packages(plotly)
#library(plotly)
#plot_ly(d1, y = ~price, color = ~neighbourhood_group, type = "box", boxmean='sd')
```


```{r, echo=FALSE}
tukeyd1 <- TukeyHSD(anovad1) #Conduct Tukey post hoc test
tukeyd1
```
To further explore the price differences among the 5 neighbourhood groups, we conduct a Tukey multiple comparisons of means test. As can be seen from the table above , there are signficant differences in mean Airbnb home prices among the 5 neighbourhood groups (p-value all smaller than 0.05), except for Staten Island and Queens (p = 0.9999811).

### 5.3 Is there a difference in mean Airbnb home price across room types?
#### H0: There is no difference in mean Airbnb price across room types.
#### H1: There is a difference in mean Airbnb price across room types.
There are three types of home for rent in this dataset:
(1) Entire home/apartment: Whole house/apartment is private.
(2) Private room: Private bedroom. Other areas are shared.
(3) Shared room: All areas (including bedrooms) are shared.
One selling point of Airbnb is that it provides a nontraditional way of lodging for travellers. The room types provided on Airbnb platform is a combination of traditional hotel and hostel. Since there are usually considerable differences in the rates of hotels and hostels, we expect to find significant differences in the means of Airbnb prices across room types. We use ANOVA to test this hypothesis. Below are the summary of the results.

```{r, include=FALSE}
summary(d$room_type)
```


```{r, echo=FALSE}
anovad2 <- aov(d$price ~ d$room_type, data=d1)
summary(anovad2)
```
As we can see from the ANOVA table above, F(2, 44667) = 15207. Since the p-value is much smaller than a significance level of 0.05, we reject the null hypothesis that there is no difference in the mean Airbnb home prices across home types and conclude that there are significant differences in the mean Airbnb price across home types.

```{r, echo=FALSE}
#Box plot with multiple room types
#plot_ly(d1, y = ~price, color = ~room_type, type = "box", boxmean='sd')
```

```{r, echo=FALSE}
tukeyd2 <- TukeyHSD(anovad2)
tukeyd2
```
Post hoc comparisons using the Tukey test was carried out. There were significant differences among mean prices of private room, entire home/apartment and shared room.

### 5.4 Is there difference in mean Airbnd home price for different neighbourhood groups and room types?
#### H0: There is no difference in mean Airbnb home price for different neighbourhood groups and room types.
#### H1: There is a difference in mean Airbnb home price for different neighbourhood groups and room types.
Taking the analysis one step further, we also investigated whether neighbourhood groups and room types interact to create an synergistic effect. Therefore, a two-way ANOVA with interaction effect was carried out.

```{r, echo=FALSE}
anovad3 <- aov(d$price ~ d$neighbourhood_group*d$room_type, data=d1)
summary(anovad3)
```
As can be seen from the above table, there was a statistically significant interaction between the effects of neighbourhood group and room types on Airbnb home price [F(8, 44655) = 24.24, p < .001]. The results indicate that there is the mean Airbnb home price varies with neighbourhood group and room type. The presence of interaction between neighbourhood group and room type means that the way Airbnb home price changes for different neighbourhood groups depends on room types. Similarly, the way Airbnb home price changes for different room types depends on neighbourhood groups. 


```{r, echo=FALSE}
install.packages("ggpubr")
library("ggpubr")
ggboxplot(d1, x = "neighbourhood_group", y = "price", color = "room_type",
          palette = c("#00AFBB", "#E7298A", "#E7B800"))
```

```{r, echo=FALSE}
TukeyHSD(anovad3)
```
A two-way ANOVA was carried out on Airbnb home prices by neighbourhood groups and room types. Since the interaction effect was statistically significant, Tukey's HSD post hoc tests were carried out. As can be seen above, most of the interactions were statistically significant (p < 0.05), but not all of them. For instance, the mean price of a private room was significantly different depending on whether it is in Manhattan or Brooklyn, but there is noevidence to suggest that the mean price of a shared room in Manhattan was significantly different from the mean price of a private room in Brooklyn (p = 0.9575967).  

## Chapter 6: Neighborhood Groups, Room Types and Availability
### 6.1 Neighborhood Groups and Availability

```{r intro, include=FALSE}
Airbnbdata <- read.csv("AB_NYC_2019.csv")
str(Airbnbdata)
```

```{r outlier, include=FALSE}
outlierKD(Airbnbdata, price,'y')
outlierKD(Airbnbdata, price,'y')
```

#### Smart Question: What is the least available neighborhood group?
Here, we are trying to anwer the question "What is the least available neighborhood group? and how can we rank their availabilities?". If we rank the Neighborhood groups based on availability, the most popular Neighborhood Group is Brooklyn, followed by Manhattan, Queens, Bronx and Staten Island respectively.

```{r boxplot, echo=FALSE}
barcolors1 = c("green", "violet", "orange", "blue", "pink", "red", "yellow", "cyan")
boxplot(availability_365~neighbourhood_group, data= Airbnbdata, main = "Neighborhood Groups Availability", col = barcolors1)
summary(Airbnbdata$neighbourhood_group)
```

If we rank the Neighborhood groups based on availability, the least available Neighborhood Group is Brooklyn, followed by Manhattan, Queens, Bronx and Staten Island respectively.

##### Brooklyn
```{r data1, echo=FALSE}
BrooklynData <- subset(Airbnbdata, neighbourhood_group == "Brooklyn" , select = 1:16)
summary(BrooklynData$availability_365)

```

Lets look at the least availabile neighborhood group, Brooklyn. The median for Brooklyn is 28 days, meaning half of the neighborhoods in Brooklyn's availability is less than 28 days of the 365days. In short, it is available ```r (28/365)*100``` % of the time.

##### Manhattan
```{r data2, echo=FALSE}
ManhattanData <- subset(Airbnbdata, neighbourhood_group == "Manhattan" , select = 1:16)
summary(ManhattanData$availability_365)
```

Lets look at the second least availabile neighborhood group, Manhattan The median for Manhattan is 36 days, meaning half of the neighborhoods in Manhattan's availability is less than 36 days of the 365days. In short, it is available ```r (36/365)*100``` % of the time.

##### Queens
```{r data3, echo=FALSE}
QueensData <- subset(Airbnbdata, neighbourhood_group == "Queens" , select = 1:16)
summary(QueensData$availability_365)
```

Lets look at the third least availabile neighborhood group, Queens The median for Queens is 98 days, meaning half of the neighborhoods in Queens's availability is less than 98 days of the 365days. In short, it is available ```r (98/365)*100``` % of the time.

##### Bronx
```{r data4, echo=FALSE}
BronxData <- subset(Airbnbdata, neighbourhood_group == "Bronx" , select = 1:16)
summary(BronxData$availability_365)
```

Lets look at the fourth least availabile neighborhood group, Bronx The median for Bronx is 148 days, meaning half of the neighborhoods in Bronx's availability is less than 148 days of the 365days. In short, it is available ```r (148/365)*100``` % of the time.

##### Staten Island
```{r data5, echo=FALSE}
StatenIslandData <- subset(Airbnbdata, neighbourhood_group == "Staten Island" , select = 1:16)
summary(StatenIslandData$availability_365)
```

Lets look at the most availabile neighborhood group, Staten Island The median for Staten Island is 219 days, meaning half of the neighborhoods in Staten Island's availability is less than 219 days of the 365days. In short, it is available ```r (219/365)*100``` % of the time.

### 6.1.1 ANOVA and Tukey for Neighborhood Group and Availability
#### Smart Question: Are the differences between availabilities significant? 
Based on the information in their availabilities, are the difference significant enough accross the neighborhood groups?
```{r AN, include=FALSE}
set.seed(1234)
dplyr::sample_n(Airbnbdata, 10)
Airbnbdata$neighbourhood_group <- ordered(Airbnbdata$neighbourhood_group,
                         levels = c("Bronx", "Brooklyn", "Manhattan", "Queens", "Staten Island"))

library(dplyr)
group_by(Airbnbdata, neighbourhood_group) %>%
  summarise(
    count = n(),
    mean = mean(availability_365, na.rm = TRUE),
    sd = sd(availability_365, na.rm = TRUE)
  )
```

```{r AN2, echo=FALSE}
AnnovaNGroupAvail <- aov(availability_365 ~ neighbourhood_group, data = Airbnbdata)
summary(AnnovaNGroupAvail)
```

```{r, echo=FALSE}
tk <- TukeyHSD(AnnovaNGroupAvail)
tk
```
We can see the variation of the means and medians of availabilities of each neighborhood group and we perforemed ANNOVA testing to see if there is a true difference between these values. We found out that the p-value is less than 0.05 and there fore we reject the null hypothesis. This means there is a significant difference between the neighborhood groups in terms of their availability.

We also performend a tukey test, and we can see that the p-values are less than 0.5 which means their variations are significant.


### 6.2 Room Types and Availability
#### Smart Question: What is the most available type of room?
```{r RM0, echo=FALSE}
boxplot(availability_365~room_type, data= Airbnbdata, main = "Room Type Availability", col = barcolors1)
summary(Airbnbdata$room_type)
```
We see the number of data collected for each room type.
Based on room type, the most available is a shared room. Private rooms and Entire Homes/Apartments are almost equally available. We will also determine if the difference in means is significant.


##### Entire Home Availability
```{r RM2, echo=FALSE}
EntireHomeData <- subset(Airbnbdata, room_type == "Entire home/apt" , select = 16)
summary(EntireHomeData)
```

##### Private Room Availability
```{r RM1, echo=FALSE}
PrivateRoomData <- subset(Airbnbdata, room_type == "Private room" , select = 16)
summary(PrivateRoomData)
```

##### Shared Home Availability
```{r RM3, echo=FALSE}
SharedRoomData <- subset(Airbnbdata, room_type == "Shared room" , select = 16)
summary(SharedRoomData)
```


### 6.2.1 ANNOVA and Tukey for Room Type and Availability
#### Smart Question: Are the differences between availabilities significant? 
```{r AA, include=FALSE}
set.seed(1234)
dplyr::sample_n(Airbnbdata, 10)
Airbnbdata$room_type <- ordered(Airbnbdata$room_type,
                         levels = c("Entire home/apt", "Private room", "Shared room"))

library(dplyr)
group_by(Airbnbdata, room_type) %>%
  summarise(
    count = n(),
    mean = mean(availability_365, na.rm = TRUE),
    sd = sd(availability_365, na.rm = TRUE)
  )
```

```{r AA2, echo=FALSE}
AnnovaRTypeAvail <- aov(availability_365 ~ room_type, data = Airbnbdata)
summary(AnnovaRTypeAvail)

tk2 <- TukeyHSD(AnnovaRTypeAvail)
tk2
```


We can see the variation of the means and medians of availabilities of each room type and we perforemed ANNOVA testing to see if there is a true difference between these values. We found out that the p-value is less than 0.05 and there fore we reject the null hypothesis. This means there is a significant difference between the room types in terms of their availability.

We also performend a tukey test, and we can see that the p-value for private room and entire home is more than 0.5. Their variations are insignificant and there is no true difference between their means.

References
Airbnb. (n.d.). What do the different home types mean? Retrieved from https://www.airbnb.com/help/article/317/what-do-the-different-home-types-mean
Bivens, J. (2019). The economic costs and benefits of Airbnb. Retrieved from https://www.epi.org/publication/the-economic-costs-and-benefits-of-airbnb-no-reason-for-local-policymakers-to-let-airbnb-bypass-tax-or-regulatory-obligations/
Nath, T. (2019). Airbnb vs. Hotels: What's the Difference? Retrieved from https://www.investopedia.com/articles/investing/112414/airbnb-brings-sharing-economy-hotels.asp
Worldatlas. (n.d.). The Boroughs Of New York City – NYC Boroughs Map: Information about the five NYC boroughs: Staten Island, Manhattan, the Bronx, and Brooklyn. Retrieved from https://www.worldatlas.com/articles/the-boroughs-of-new-york-city.html


